An efficient acyclic contact planner for multiped robots

### 2015-12-31 body/intro.tex
citation tedrake

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches was proposed \citep{Mordatch:2012:DCB:2185520.2185539} and successfully applied to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \citeauthor{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. Aside from the computation cost, a major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.

>>>>

Most of the papers that followed the work of \citeauthor{conf/iser/BretlRLKA04} have explored alternative formulations to handle the combinatorial issue. Two main directions have been explored. \textbf{On one hand, local optimization of both the root trajectory \Pa and the contact positions $\mathcal{P}_2$} has been used, to trade the combinatorial of the complete problem for a differential complexity, at the cost of local convergence. A complete example of the potential offered by such approaches was proposed \citep{Mordatch:2012:DCB:2185520.2185539} and successfully applied to a real robot \citep{mordatch2015}. To keep reasonable computation times, the method uses a simplified dynamic model for the avatar. Still, the computation time is far from interactive  (about 1 minute of computation for a sequence of 20 contacts). \citeauthor{DBLP:conf/humanoids/DeitsT14} propose to solve contact planning globally as a mixed integer problem, but only cyclic, bipedal locomotion is considered. 
\citeauthor{dai2014whole} extend the work of \citeauthor{Posa:2014:DMT:2568343.2568352} to discover the short contact sequence for landing motions, but specify
the contacts manually for more complex interactions.
A major drawback of these optimization based approaches is thus that they only offer local convergence when applied to acyclic contact planning.
